CRUSE to Safe Cycling in Ireland

### 2023-09-25 paper.qmd
City Caulfield et al 2012

<!-- ## National results {#sec-national-results}

@@

Local -->

<!-- ## Local results -->

@@

::: {#fig-city-results}

![](images/rnet_types.png)

Fastest, balanced and quietest cycle networks within 3km circular areas containing the four largest cities in Ireland.
The networks are coloured by cycle friendliness and with widths varying in proportion to the potential level of cycling under the 'Go Dutch' scenario.

:::

@@

Although Dublin City has made progress, there are still many parts of the Fastest route network, and even some parts of the Balanced and Quietest route networks, that are not cycle friendly and which have high cycling potential.
According to a recent report, 71% of residents in the Dublin Metropolitan Area support "more cycle tracks along roads, physically separated
from traffic and pedestrians".^[
https://www.nationaltransport.ie/wp-content/uploads/2022/05/220504-WACI22_DublinMetropolitanArea_v35_DIGITAL_v2.pdf
]
The results for the Dublin area could help prioritise investment in cycling infrastructure in the city.

@@

As highlighted in a paper on cycling infrastructure preferences based on a case study of Dublin, both directness and quietness are important :

> Direct routes with short journey times were found to be the most important positive variable for existing cyclists and non-cyclists in determining route choice. This is followed by infrastructure type, the number of junctions along the route, traffic speed and cyclist volumes. In terms if infrastructure, regardless of the level of cycling confidence, routes which have ‘no facilities’ or ‘bus/cycle lanes’ are the least favoured cycle route types.

The CRUSE tool can help both in terms of describing the current situation, and also prioritise investment in those routes lacking infrastructure highlighted by  as being least favoured by cyclists.

>>>>

```{=html}
<!-- ## National results {#sec-national-results}

@@

Local -->
```
<!-- ## Local results -->

@@

::: {#fig-city-results}
![](images/rnet_types.png)

Fastest, balanced and quietest cycle networks within 3km circular areas containing the four largest cities in Ireland.
The networks are coloured by cycle friendliness and with widths varying in proportion to the potential level of cycling under the 'Go Dutch' scenario.
:::

@@

Although Dublin City has made progress, there are still many parts of the Fastest route network, and even some parts of the Balanced and Quietest route networks, that are not cycle friendly and which have high cycling potential.
According to a recent report, 71% of residents in the Dublin Metropolitan Area support "more cycle tracks along roads, physically separated from traffic and pedestrians".[^8]
The results for the Dublin area could help prioritise investment in cycling infrastructure in the city.

[^8]:  https://www.nationaltransport.ie/wp-content/uploads/2022/05/220504-WACI22_DublinMetropolitanArea_v35_DIGITAL_v2.pdf

@@

As highlighted in a paper on cycling infrastructure preferences based on a case study of Dublin, both directness and quietness are important [@caulfield2012]:

> Direct routes with short journey times were found to be the most important positive variable for existing cyclists and non-cyclists in determining route choice.
> This is followed by infrastructure type, the number of junctions along the route, traffic speed and cyclist volumes.
> In terms if infrastructure, regardless of the level of cycling confidence, routes which have 'no facilities' or 'bus/cycle lanes' are the least favoured cycle route types.

The CRUSE tool can help both in terms of describing the current situation, and also prioritise investment in those routes lacking infrastructure highlighted by @caulfield2012 as being least favoured by cyclists.
